
Define multiplot function - this function prints multiple plots (created using ggplot function) on one page

```{r}
multiplot <- function(..., plotlist = NULL, file, cols = 1, layout = NULL) {
  require(grid)

  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  if (is.null(layout)) {
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

  if (numPlots == 1) {
    print(plots[[1]])

  } else {
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    for (i in 1:numPlots) {
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

````

Mid-year Survey Analysis by Demographic Data 
========================================================

Set directory and read file format - csv - need to be filtered by question group so only questions relating to Aspire selected. Then create fields to define positive responses and those that should be counted towards toal responses

```{r}
setwd("~/Work Docs/Godzilla/Equity Analysis")

mydata_all<-read.csv("midyearsurvey_1314.csv",sep=",",header=TRUE)


mydata_aspire<-subset(mydata_all,QuestionGroup=='Affiliation'| 
                                        QuestionGroup=='Gallup Q12 (Engagement)' |                                 
                                        QuestionGroup=='Job Satisfaction' |
                                        QuestionGroup=='Retention' |
                                        QuestionGroup=='Site Culture' |
                                        QuestionGroup=='Understanding Priorities & Policies')

##creating age groups
mydata_aspire$agegroup<-cut(mydata_aspire$Respondent_Age_FromHR,c(20,30,40,50,100) )

questionfields<-c('Affiliation','Gallup Q12 (Engagement)','Job Satisfaction','Retention','Site Culture','Understanding Priorities & Policies')



response.set<-which(mydata_aspire$Response_Numeric>0)

#reverse the sequence for negative questions
mydata_aspire$Response_Numeric[which(mydata_aspire$QuestionCommonID==152|mydata_aspire$QuestionCommonID==153)]=6-mydata_aspire$Response_Numeric[which(mydata_aspire$QuestionCommonID==152|mydata_aspire$QuestionCommonID==153)]

#create concatenated school type and region
mydata_aspire$schoolcomb<-paste(mydata_aspire$Respondent_Region_FromHR,mydata_aspire$SchoolType)
schooltypefields<-unique(mydata_aspire$schoolcomb)



```


List out the different demographic variables we are basing our analysis off:
```{r}
demogvar<-c("Respondent_Gender_FromHR","EthnicGroup","JobGroup","agegroup")
labelvar<-c("gender","race","job","age")


```



```{r}
require(ggplot2)

plot<-vector('list',length(questionfields)*4)
#plot$race<-vector('list',length(questionfields))

for (var in 1:4) {
##paste("plot",labelvar[var])<-vector('list',length(questionfields))
varselect<-demogvar[var]
varlevels<-levels(mydata_aspire[[varselect]])

  for (i in 1:length(questionfields)) {
    qgroup<-questionfields[i]
    qgroup.set<-response.set[which(mydata_aspire$QuestionGroup[response.set]==qgroup)]
    qgroup.mean<-rep(NA,length(varlevels))
    qgroup.se<-rep(NA,length(varlevels))
    
      for (j in 1:length(varlevels)) {   
          levelj<-varlevels[j]
          qgroup.var.set<-qgroup.set[which(mydata_aspire[[varselect]][qgroup.set]==levelj)]
          qgroup.mean[j]<-mean(mydata_aspire$Response_Numeric[qgroup.var.set])
          qgroup.se[j]<-1.96*sd(mydata_aspire$Response_Numeric[qgroup.var.set])/sqrt(length(mydata_aspire$Response_Numeric[qgroup.var.set]))    ## divide standard error by sqrt of n - to adjust for variation of averages
      }
      df<-data.frame(varlevels,qgroup.mean,qgroup.se)
      limits<-aes(ymax=qgroup.mean+qgroup.se,ymin=qgroup.mean-qgroup.se)
      p<-ggplot(df,aes(x=varlevels,y=qgroup.mean,ymin=3,ymax=5),)+ggtitle(paste(labelvar[var],":",qgroup))+theme(axis.text.x=element_text(angle=-90))+xlab(" ") + ylab("avg response")
      plot[[(var-1)*6+i]]=p+geom_point(aes(colour=varlevels,size=20))+geom_errorbar(limits,width=0.2)+theme(legend.position="none")
    }
}

multiplot(plotlist=c(plot),cols=4)

```

Create table that looks at percentage of positive responses


```{r}

plot<-vector('list',length(questionfields)*4)
#plot$race<-vector('list',length(questionfields))

for (var in 1:4) {
##paste("plot",labelvar[var])<-vector('list',length(questionfields))
varselect<-demogvar[var]
varlevels<-levels(mydata_aspire[[varselect]])

  for (i in 1:length(questionfields)) {
    qgroup<-questionfields[i]
    qgroup.set<-response.set[which(mydata_aspire$QuestionGroup[response.set]==qgroup)]
    qgroup.mean<-rep(NA,length(varlevels))
    qgroup.se<-rep(NA,length(varlevels))
    
      for (j in 1:length(varlevels)) {   
          levelj<-varlevels[j]
          qgroup.var.set<-qgroup.set[which(mydata_aspire[[varselect]][qgroup.set]==levelj)]
          qgroup.mean[j]<-mean(I(mydata_aspire$Response_Numeric[qgroup.var.set]>3))
          qgroup.se[j]<-1.96*(qgroup.mean[j])*(1-qgroup.mean[j])/sqrt(length(mydata_aspire$Response_Numeric[qgroup.var.set]))    ## divide standard error by sqrt of n - to adjust for variation of averages
      }
      df<-data.frame(varlevels,qgroup.mean,qgroup.se)
      limits<-aes(ymax=qgroup.mean+qgroup.se,ymin=qgroup.mean-qgroup.se)
      dodge<-position_dodge(width=0.4)
      p<-ggplot(df,aes(x=varlevels,y=qgroup.mean,ymin=0.5,ymax=1),)+ggtitle(paste(labelvar[var],":",qgroup))+theme(axis.text.x=element_text(angle=-90))+xlab(" ") + ylab("% positive")
      plot[[(var-1)*6+i]]=p+geom_point(aes(colour="grey50",size=40,shape=varlevels))+geom_errorbar(limits,width=0.2)+theme(legend.position="none")
    }
}

multiplot(plotlist=c(plot),cols=4)


##use this code to check  job satisfaction overall % correct data against data set
i=3
    qgroup<-questionfields[i]
    qgroup.set<-response.set[which(mydata_aspire$QuestionGroup[response.set]==qgroup)]
 table(mydata_aspire$Response_Numeric[qgroup.set])
mean(I(mydata_aspire$Response_Numeric[qgroup.set]>3))

```


This script produces question-specific plots. choose the demogrpahic variable by setting var and choose the question group by selecting i



```{r}
require(ggplot2)

grouptoID<-data.frame(table(mydata_aspire$QuestionCommonID,mydata_aspire$QuestionGroup)) #create` a question group to common ID reference

#plot$race<-vector('list',length(questionfields))


# manually set var 1=gender ; 2=ethnic group ; 3= job group ; 4=age group
var=4

varselect<-demogvar[var]
varlevels<-levels(mydata_aspire[[varselect]])

# manually set questionfield - 1=affiliation ; 2 = engagement ; 3 = job statisfaction ; 4 = retention ; 5=site culture ;; 6= priorities
i=4

  qgroup<-questionfields[i]
  qcommonid<- subset(grouptoID,subset = Var2==qgroup & Freq>0)$Var1
    

  #define length based on list of questions
  plot<-vector('list',length(qcommonid))


for (k in 1:length(qcommonid)) {
            qid<-qcommonid[k]  
            qgroup.set<-response.set[which(mydata_aspire$QuestionCommonID[response.set]==qid)]
            qtext<-substr(mydata_aspire$QuestionText_Cleaned[qgroup.set][1],1,60)
            qgroup.mean<-rep(NA,length(varlevels))
            qgroup.se<-rep(NA,length(varlevels))
      
              for (j in 1:length(varlevels)) {   
                  levelj<-varlevels[j]
                  qgroup.var.set<-qgroup.set[which(mydata_aspire[[varselect]][qgroup.set]==levelj)]
                  qgroup.mean[j]<-mean(mydata_aspire$Response_Numeric[qgroup.var.set])
                  qgroup.se[j]<-1.96*sd(mydata_aspire$Response_Numeric[qgroup.var.set])/sqrt(length(mydata_aspire$Response_Numeric[qgroup.var.set]))   
                  ## divide standard error by sqrt of n - to adjust for variation of averages
              }
   
            df<-data.frame(varlevels,qgroup.mean,qgroup.se)
            limits<-aes(ymax=qgroup.mean+qgroup.se,ymin=qgroup.mean-qgroup.se)
            p<-ggplot(df,aes(x=varlevels,y=qgroup.mean,ymin=3,ymax=5),)+ggtitle(paste(labelvar[var],":",qgroup,";",qid,qtext))
            plot[[k]]=p+geom_point(aes(colour=varlevels,size=20))+geom_errorbar(limits,width=0.2)+theme(legend.position="none")     
        }
    
multiplot(plotlist=c(plot),cols=2)



```


The next steps looks at the teacher level differences between different school type/regions 



```{r}
require(ggplot2)

grouptoID<-data.frame(table(mydata_aspire$QuestionCommonID,mydata_aspire$QuestionGroup)) #create` a question group to common ID reference

#plot$race<-vector('list',length(questionfields))


# manually set var 1=gender ; 2=ethnic group ; 3= job group ; 4=age group
var=3
varselect<-demogvar[var]
varlevels<-levels(mydata_aspire[[varselect]])
groupselect<-varlevels[7] #select teacher group - #7 
  

# manually set questionfield - 1=affiliation ; 2 = engagement ; 3 = job statisfaction ; 4 = retention ; 5=site culture ;; 6= priorities
i=3

  qgroup<-questionfields[i]
  qcommonid<- subset(grouptoID,subset = Var2==qgroup & Freq>0)$Var1
   

  #define length based on list of questions
  plot<-vector('list',length(qcommonid))



for (k in 1:length(qcommonid)) {
            qid<-qcommonid[k]  
            qgroup.set<-response.set[which(mydata_aspire$QuestionCommonID[response.set]==qid)]
            qtext<-substr(mydata_aspire$QuestionText_Cleaned[qgroup.set][1],1,60)
            qgroup.mean<-rep(NA,length(schooltypefields))
            qgroup.se<-rep(NA,length(schooltypefields))
      
              for (j in 1:length(schooltypefields)) {   
                  schoolj<-schooltypefields[j]
                  qgroup.var.set<-qgroup.set[which(mydata_aspire[[varselect]][qgroup.set]==groupselect)]
                  qgroup.var.set2<-qgroup.var.set[which(mydata_aspire[["schoolcomb"]][qgroup.var.set]==schoolj)]         
                  qgroup.mean[j]<-mean(mydata_aspire$Response_Numeric[qgroup.var.set2])
                  qgroup.se[j]<-1.96*sd(mydata_aspire$Response_Numeric[qgroup.var.set2])/sqrt(length(mydata_aspire$Response_Numeric[qgroup.var.set2]))   
                  ## divide standard error by sqrt of n - to adjust for variation of averages
              }
   
            df<-data.frame(schooltypefields,qgroup.mean,qgroup.se)
            limits<-aes(ymax=qgroup.mean+qgroup.se,ymin=qgroup.mean-qgroup.se)
            p<-ggplot(df,aes(x=schooltypefields,y=qgroup.mean,ymin=1,ymax=5),)+ggtitle(paste(groupselect,":",qgroup,";",qid,qtext))+theme(axis.text.x=element_text(angle=-90))+xlab(" ")+ylab("avg response")+xlab("")
             plot[[k]]=p+geom_point(aes(colour=schooltypefields,size=20))+geom_text(aes(label=schooltypefields,colour=schooltypefields),size=3,angle=45,vjust=-3)+geom_errorbar(limits,width=0.2)+theme(legend.position="none")     
        }
    
multiplot(plotlist=c(plot),cols=2)

   


```





```{r}
require("gee")
  # gee allow generalized estimation equation wtih 

# manually set var 1=gender ; 2=ethnic group ; 3= job group ; 4=age group
var=3
varselect<-demogvar[var]
varlevels<-levels(mydata_aspire[[varselect]])
groupselect<-varlevels[7] #select teacher group - #7 
  

# manually set questionfield - 1=affiliation ; 2 = engagement ; 3 = job statisfaction ; 4 = retention ; 5=site culture ;; 6= priorities
i=3

  qgroup<-questionfields[i]
  qcommonid<- subset(grouptoID,subset = Var2==qgroup & Freq>0)$Var1



```

read in 

```{r}

data_allyears<-read.csv("allsurvey_1213_1314.csv",sep=",",header=TRUE)


data_allyears<-subset(data_allyears,QuestionGroup=='Affiliation'| 
                                        QuestionGroup=='Gallup Q12 (Engagement)' |                                 
                                        QuestionGroup=='Job Satisfaction' |
                                        QuestionGroup=='Retention' |
                                        QuestionGroup=='Site Culture' |
                                        QuestionGroup=='Understanding Priorities & Policies')


###pick out the survey interested
###12-13 mid year = 20 ; 12-13 end of year =21
data_allyears<-subset(data_allyears,SurveyID==21)


##creating age groups
data_allyears$agegroup<-cut(data_allyears$Respondent_Age_FromHR,c(20,30,40,50,100))

questionfields<-c('Affiliation','Gallup Q12 (Engagement)','Job Satisfaction','Retention','Site Culture','Understanding Priorities & Policies')


response.set.all<-which(data_allyears$Response_Numeric>0)

#reverse the sequence for negative questions
data_allyears$Response_Numeric[which(data_allyears$QuestionCommonID==152|data_allyears$QuestionCommonID==153)]=6-data_allyears$Response_Numeric[which(data_allyears$QuestionCommonID==152|data_allyears$QuestionCommonID==153)]

#create concatenated school type and region
data_allyears$schoolcomb<-paste(data_allyears$Respondent_Region_FromHR,data_allyears$SchoolType)
schooltypefields<-unique(data_allyears$schoolcomb)

#list our the variables 
demogvar<-c("Respondent_Gender_FromHR","EthnicGroup","JobGroup","agegroup")
labelvar<-c("gender","race","job","age")




grouptoID<-data.frame(table(mydata_aspire$QuestionCommonID,mydata_aspire$QuestionGroup)) #create` a question group to common ID reference

#plot$race<-vector('list',length(questionfields))


# manually set var 1=gender ; 2=ethnic group ; 3= job group ; 4=age group
var=3
varselect<-demogvar[var]
varlevels<-levels(mydata_aspire[[varselect]])
groupselect<-varlevels[7] #select teacher group - #7 
  

# manually set questionfield - 1=affiliation ; 2 = engagement ; 3 = job statisfaction ; 4 = retention ; 5=site culture ;; 6= priorities
i=3

  qgroup<-questionfields[i]
  qcommonid<- subset(grouptoID,subset = Var2==qgroup & Freq>0)$Var1
   

  #define length based on list of questions
  plot<-vector('list',length(qcommonid))



for (k in 1:length(qcommonid)) {
            qid<-qcommonid[k]  
            qgroup.set<-response.set.all[which(data_allyears$QuestionCommonID[response.set.all]==qid)]
            qtext<-substr(data_allyears$QuestionText_Cleaned[qgroup.set][1],1,60)
            qgroup.mean<-rep(NA,length(schooltypefields))
            qgroup.se<-rep(NA,length(schooltypefields))
      
            if (length(qgroup.set)==0) { next }
            
            else {
                 for (j in 1:length(schooltypefields)) {   
                    schoolj<-schooltypefields[j]
                    qgroup.var.set<-qgroup.set[which(data_allyears[[varselect]][qgroup.set]==groupselect)]
                    qgroup.var.set2<-qgroup.var.set[which(data_allyears[["schoolcomb"]][qgroup.var.set]==schoolj)]         
                    qgroup.mean[j]<-mean(data_allyears$Response_Numeric[qgroup.var.set2])
                    qgroup.se[j]<-1.96*sd(data_allyears$Response_Numeric[qgroup.var.set2])/sqrt(length(data_allyears$Response_Numeric[qgroup.var.set2]))   
                    ## divide standard error by sqrt of n - to adjust for variation of averages
                }
     
            df<-data.frame(schooltypefields,qgroup.mean,qgroup.se)
            limits<-aes(ymax=qgroup.mean+qgroup.se,ymin=qgroup.mean-qgroup.se)
            p<-ggplot(df,aes(x=schooltypefields,y=qgroup.mean,ymin=1,ymax=5),)+ggtitle(paste(groupselect,":",qgroup,";",qid,qtext))+theme(axis.text.x=element_text(angle=-90))+xlab(" ")+ylab("avg response")+xlab("")
             plot[[k]]=p+geom_point(aes(colour=schooltypefields,size=20))+geom_text(aes(label=schooltypefields,colour=schooltypefields),size=3,angle=45,vjust=-3)+geom_errorbar(limits,width=0.2)+theme(legend.position="none")                
              
              
            }       
              
        }
    
multiplot(plotlist=c(plot),cols=2)

   



```
